\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{braket, units, enumitem}
\usepackage{todonotes}

\begin{document}

\renewcommand{\b}[1]{\textbf{#1}}
\newcommand{\insight}[1]{\b{Insight:} \textit{#1}}
\newcommand{\actionable}[1]{\todo{#1}}


\nocite{*}

\title{CS 486}

\author{Alexander Maguire \\
amaguire@uwaterloo.ca \\
20396195}

\maketitle

\section{Administration}
John Doucette j3doucet@uwaterloo.ca \\
\textbf{Office Hours:} Thursdays 10:15-11:15 DC 2580 \\
http://www.cs.uwaterloo.ca/~klarson/teaching/W15-486

\textbf{Required Text:} Russell, Norving - AI: A Modern Approach (3rd Edition) \\
\textbf{Additional Text}: AI: Foundations of Computation Agents, Poole and Mackworth

\subsection{Evaluation}
6 Assignments: 60\% \\
Final: 40\% \\
Project (optional): up to 5\% (group of 3) \\
\\
Assignments will be accepted after 48h, but never afterwards. \\
\\
Daily quizzes, related to material. Work in pairs or trios. John says this is for pedagogical reasons and he seems to
know what he's talking about, so that's pretty cool! \\
\\
\b{Do the assigned readings EVERY DAY before class. Expect 15 to 30 minutes.}




\section{Introduction}
\textit{Unlikely to be on the exam.}

What is AI?

Definitions differ along two axes:
\begin{enumerate}
    \item reason vs behavior
    \item human vs rational
\end{enumerate}

Human-side: Turing test. yada yada yada. Straw vulcan. yada yada yada.

\insight{Historically, humans have always thought the brain was like the most technologically advanced computation system they
had available. Like a printing press, loom, or telephone exchange.}

\actionable{Refresh basic statistics}



\subsection{Rational Agents}
By definition, anything that exists in an environment, with a body, sensors, actuators, and a logic unit.
Properties of a task environment involve
\begin{enumerate}
    \item fully observable vs partially observable
    \item deterministic vs stochastic
    \item episodic (end condition) vs dynamic
    \item discrete vs continuous
    \item single vs multiple agents
\end{enumerate}

\subsection{State of the Art}
\actionable{John did a project on translation.}
BOOOORING



\end{document}
